Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-20 paper/paper.qmd
commit qmd file

The results highlight the geographic divide between the two candidates. Trump is predicted to perform well in southern and midwestern states, where his polling averages are significantly higher. Harris, on the other hand, is projected to win in the Midwest and along the East Coast, with stronger polling percentages in traditionally Democratic-leaning regions.

```{r}
#| label: fig-statemap
#| fig-cap: Predicted Winner of 2024 US Presidential Election by State
#| echo: false
#| warning: false
#| message: false
#| cache: false

@@

In swing states like North Carolina and Nevada, where the polling percentages are closer, Trump is still predicted to win with probabilities of 94.36% and 51.23%, respectively. These battleground states show tighter polling averages and thus greater uncertainty in the predicted outcomes.

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Predicted 2024 US Presidential Election outcomes by state, based on polling percentages for Trump and Harris"
#| warning: false

@@

The results of our predictive model suggest that Donald Trump is likely to win key states such as Florida, Missouri, and Montana, while Kamala Harris is expected to secure victories in states like Michigan, Virginia, and Pennsylvania. Close contests are predicted in battleground states like Nevada and North Carolina, where Trump holds a slight edge.

>>>>

The results highlight the geographic divide between the two candidates. Trump is predicted to perform well in southern and midwestern states, where his polling averages are significantly higher. Harris, on the other hand, is projected to win in the Midwest and along the East Coast, with stronger polling percentages in traditionally Democratic-leaning regions.
```{r}
#| label: fig-statemap
#| fig-cap: Predicted Winner of 2024 US Presidential Election by State
#| echo: false
#| warning: false
#| message: false
#| cache: false

@@

In swing states like North Carolina and Nevada, where the polling percentages are closer, Trump is still predicted to win with probabilities of 94.36% and 51.23%, respectively. These battleground states show tighter polling averages and thus greater uncertainty in the predicted outcomes.
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Predicted 2024 US Presidential Election outcomes by state, based on polling percentages for Trump and Harris"
#| warning: false

@@

```
The results of our predictive model suggest that Donald Trump is likely to win key states such as Florida, Missouri, and Montana, while Kamala Harris is expected to secure victories in states like Michigan, Virginia, and Pennsylvania. Close contests are predicted in battleground states like Nevada and North Carolina, where Trump holds a slight edge.
